Compositional equivalences based on Open pNets

### 2021-10-12 2016-Weak-FH-Bisim/WeakBisim.tex
subseteq

\begin{theorem}[Congruence for  weak bisimulation]\label{weak-thm-congr-eq}
	Consider an open pNet $P$
 that cannot observe silent actions, of the form 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\set{\symb{SV}}\myrangle$.
	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $Q'$ be two weak FH-bisimilar pNets such that\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
	ensured by 
	weak bisimilarity.} 
	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$. Then 
	$\pNet[\pNetQ]_{j_0}$ and 
	$\pNet[\pNetQ']_{j_0}$ are weak FH-bisimilar.
\end{theorem}

\begin{theorem}[Context equivalence for  weak bisimulation]\label{weak-thm-ctxt-eq}
	Consider two  open pNets
	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
	\Sort_j^{j\in 
	J}, 	\set{\symb{SV'}}\myrangle$ that are weak FH-bisimilar
	(recall they must have the same holes to be bisimilar) and that cannot observe silent actions.
	Let $j_0\in J$ be a hole, and $\pNetQ$ be a pNet such that $\Sortop(\pNetQ)=\Sort_{j_0}$. Then 
	$\pNet[\pNetQ]_{j_0}$ and 
	$\pNet'[\pNetQ]_{j_0}$ are weak FH-bisimilar.
\end{theorem}

@@

 \subsection{Proof of Theorem ~\ref{thm-congr-eq}}~\\
\noindent{\bf  Congruence}:
\textit{	Consider an open pNet:
	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\set{\symb{SV}}\myrangle$.
	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two FH-bisimilar pNets such that 
	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
	ensured by 
	strong bisimilarity.}. Then 
	$\pNet[\pNetQ]_{j_0}$ and 
	$\pNet[\pNetQ']_{j_0}$ are FH-bisimilar.
}
\medskip
\begin{proof}
 The proof of Theorem~\ref{thm-congr-eq} exhibits classically a bisimulation relation for 
 a 
 composed system.  It considers then an open transition of $P[Q]_{j_0}$ that should be 
 simulated. It then uses  Lemma~\ref{lem-decompose} to decompose the open transition 
 of $P[Q]_{j_0}$ and obtain an open transition of $P$ and $Q$; the FH-bisimulation 
 property can 
 be applied  to $Q$ to obtain an equivalent family of open transitions of $Q'$; this 
 family is 
 then recomposed by Lemma~\ref{lem-compose} to build a set of open transitions of 
 $P[Q']_{j_0}$ 
 that will simulate the original one.

@@

        \subsection{Proof of Theorem ~\ref{thm-ctxt-eq}: Context equivalence}
\textit{	Consider two FH-bisimilar open pNets:
	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
	\Sort_j^{j\in 
	J}, 	\set{\symb{SV'}}\myrangle$ 
	(recall they must have the same holes to be bisimilar).
	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
	$\pNet[Q]_{j_0}$ and 
	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
}

>>>>

\begin{theorem}[Congruence for  weak bisimulation]\label{weak-thm-congr-eq}
	Consider an open pNet $P$
 that cannot observe silent actions, of the form 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\set{\symb{SV}}\myrangle$.
	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $Q'$ be two weak FH-bisimilar pNets such that\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
	ensured by 
	weak bisimilarity.} 
	$\Sortop(\pNetQ)=\Sortop(\pNetQ')\subseteq\Sort_{j_0}$. Then 
	$\pNet[\pNetQ]_{j_0}$ and 
	$\pNet[\pNetQ']_{j_0}$ are weak FH-bisimilar.
\end{theorem}

\begin{theorem}[Context equivalence for  weak bisimulation]\label{weak-thm-ctxt-eq}
	Consider two  open pNets
	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
	\Sort_j^{j\in 
	J}, 	\set{\symb{SV'}}\myrangle$ that are weak FH-bisimilar
	(recall they must have the same holes to be bisimilar) and that cannot observe silent actions.
	Let $j_0\in J$ be a hole, and $\pNetQ$ be a pNet such that $\Sortop(\pNetQ)\subseteq\Sort_{j_0}$. Then 
	$\pNet[\pNetQ]_{j_0}$ and 
	$\pNet'[\pNetQ]_{j_0}$ are weak FH-bisimilar.
\end{theorem}

@@

 \subsection{Proof of Theorem ~\ref{thm-congr-eq}}~\\
\noindent{\bf  Congruence}:
\textit{	Consider an open pNet:
	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\set{\symb{SV}}\myrangle$.
	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two FH-bisimilar pNets such that 
	$\Sortop(\pNetQ)=\Sortop(\pNetQ')\subseteq\Sort_{j_0}$\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
	ensured by 
	strong bisimilarity.}. Then 
	$\pNet[\pNetQ]_{j_0}$ and 
	$\pNet[\pNetQ']_{j_0}$ are FH-bisimilar.
}
\medskip
\begin{proof}
 The proof of Theorem~\ref{thm-congr-eq} exhibits classically a bisimulation relation for 
 a 
 composed system.  It considers then an open transition of $P[Q]_{j_0}$ that should be 
 simulated. It then uses  Lemma~\ref{lem-decompose} to decompose the open transition 
 of $P[Q]_{j_0}$ and obtain an open transition of $P$ and $Q$; the FH-bisimulation 
 property can 
 be applied  to $Q$ to obtain an equivalent family of open transitions of $Q'$; this 
 family is 
 then recomposed by Lemma~\ref{lem-compose} to build a set of open transitions of 
 $P[Q']_{j_0}$ 
 that will simulate the original one.

@@

        \subsection{Proof of Theorem ~\ref{thm-ctxt-eq}: Context equivalence}
\textit{	Consider two FH-bisimilar open pNets:
	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
	\Sort_j^{j\in 
	J}, 	\set{\symb{SV'}}\myrangle$ 
	(recall they must have the same holes to be bisimilar).
	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)\subseteq\Sort_{j_0}$. Then 
	$\pNet[Q]_{j_0}$ and 
	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
}
